Modelling Stochastic Time Delay for Regression

### 2021-03-22 documentation/article/article.tex
Changed wording
Update wording

There has been little work on \emph{stochastic time delays} i.e. time delays which vary randomly. In this paper, we deal with this specific case.

@@

% TODO: Rewrite concrete expression of support...is it on x ot t? -- Aaron: f(x(t)). Consider x(t) = 0.1 for t is odd, 1 for t is even. If f(x(t)) = 0 for t is odd, 1 for t is even then the series is still valid for our method.  
Let $x: \mathcal{D}_n\subset [a, b] \longrightarrow \mathbb{R}$, where $\mathcal{D}_n$ is a finite set of $n$ points. We want to determine the, functional relationship $f:\mathbb{R} \longrightarrow \mathbb{R}$ to some other (target) variable $y$. We further impose the extra condition for $f$ to be injective.  The series $x(t)$ must be stationary with a known value for the point at which $f(x(t)) = 0$.  That is, we know at which point the input series has no effect on the output (when it’s off). The size of the support of $f(x(t))$ should be small relative to the total vector length (we we will explore this constraint in more detail in the 'Limitations' section). We utilise the terminology {\em impulse} for an individual element of the support of $f$.

>>>>

In this paper, we deal with the specific case of \emph{stochastic time delays} i.e. time delays which vary randomly. There appears to be little existing research on this exact topic.

@@

% TODO: Rewrite concrete expression of support...is it on x ot t? -- Aaron: f(x(t)). Consider x(t) = 0.1 for t is odd, 1 for t is even. If f(x(t)) = 0 for t is odd, 1 for t is even then the series is still valid for our method.  
Let $x: \mathcal{D}_n\subset [a, b] \longrightarrow \mathbb{R}$, where $\mathcal{D}_n$ is a finite set of $n$ points. We want to determine the, functional relationship $f:\mathbb{R} \longrightarrow \mathbb{R}$ to some other (target) variable $y$. Furthermore, we impose the condition that $f$ be injective.  The series $x(t)$ must be stationary with a known value for the point at which $f(x(t)) = 0$.  That is, we know at which point the input series has no effect on the output (when it’s off). The size of the support of $f(x(t))$ should be small relative to the total vector length (we we will explore this constraint in more detail in the 'Limitations' section). We utilise the terminology {\em impulse} for an individual element of the support of $f$.
